Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-10 pkg/disttree/inst/draft/rejoinder2.Rnw
rephrased rejoinder comments regarding East Tyrol
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2460 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 18cee89968efc59466a8e2a36bda56a31e5f2230

FIXME: adaption in the manuscript

FIXME: I think we should present the two arguments more side by side, i.e., mention both
early on and subsequently discuss both in more detail. (1) One factor is that only a single
split into 28 years of training and 4 years of test data is considered in the main manuscript.
When doing the full cross-validation the pronounced differences between the methods are much
diminished. (2) East Tyrol is in a different climate zone and hence effects could be more
additive and with less interactions than in North Tyrol.

Thank you very much for your comment! East Tyrol lies in a different climate zone than the 
rest of Tyrol indicating different meteorological characteristics. For example, a covariate
might have a linear effect on the expected amount of rain in East Tyrol while it has a
non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
GAMLSS will capture this influence better than a tree model, particularly if this covariate
is correctly specified in the model (which might be the case in the prespecified GAMLSS).
Of course, these are just assumptions and there could be many other reasons. However,
looking at the results of the cross-validation in Supplement~B it can be observed that
the difference in performance between the GAMLSS and the distributional forest models as
seen in the single evaluation evens out, hence the specific choice of learning years seems
to have an impact as well.

>>>>

East Tyrol differs from North Tyrol as it is located south of the main Alpine Ridge and thus
in a different climate zone. Consequently, both long-term climatological characteristics
and precipitation patterns in 2009--2012 differ. This is not visible from Figure~8 directly,
though, and hence we added a short explanation at the end of Section~3.4

Moreover, sampling variability clearly also plays a role as the differences from Figure~8
are somewhat evened out in the cross-validation, specifically for some of the East Tyrolian 
stations. This is shown in Supplement~B and was already discussed in the corresponding
paragraph in Section~4 (Axams vs.\ other meteorological stations). Additionally, we now
include some comments on this at the end of Section~3.4 where this was admittedly lacking
in the previous version of the manuscript.

% Thank you very much for your comment! One important fact that could be a reason for the
% different results is that East Tyrol does not lie in the same climate zone as the rest of Tyrol 
% indicating different meteorological characteristics. For example, a covariate
% might have a linear effect on the expected amount of rain in East Tyrol while it has a
% non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
% GAMLSS will capture this influence better than a tree model, particularly if this covariate
% is correctly specified in the model (which might be the case in the prespecified GAMLSS).
% Of course, this is just an assumption and there could be other reasons for the performance
% difference between the GAMLSS and the distributional forest models in East Tyrol. However, 
% looking at the results of the cross-validation in Supplement~B it can be observed that this 
% difference as seen in the single evaluation evens out for several stations in East Tyrol, 
% hence the specific choice of learning and validation period seems to have an impact as well.
% These two aspects are now also discussed more in detail in the main manuscript.
